Lab News

### 2023-09-22 index.qmd
fix date in news
update news feed

<font color="#d08770">[May 26 2023].</font> **Paper accepted**.   Roth, A.M., Calalo, J.A., Lokesh, R., Sullivan, S.R., Grill, S., Jeka, J.J., van der Kooij, K., Carter, M.J, & Cashaback, J.G.A. Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds. *Proceedings of the Royal Society B*.

@@

<font color="#d08770">[June 16 2023].</font> **New preprint**. McKay, B., Corson, A.E., Seedu, J., De Faveri, C.S., Hasan, H., Arnold, K., Adams, F.C., & Carter, M.J. Reporting bias, not external focus: A robust Bayesian meta-analysis of the attentional focus literature. *SportR*$\chi$*iv*. doi: <https://doi.org/10.51224/SRXIV.304>

>>>>

<font color="#d08770">[September 22 2023].</font> **New award**. Congratulations to Daniel Deletsu who was awarded a 2-year Master's scholarship through an initiative from the Heart and Stroke Foundation of Canada, Brain Canada Foundation, and the Canadian Institutes of Health Research.

<font color="#d08770">[September 6 2023].</font> **Paper accepted**.   Roth, A.M., Calalo, J.A., Lokesh, R., Sullivan, S.R., Grill, S., Jeka, J.J., van der Kooij, K., Carter, M.J, & Cashaback, J.G.A. Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds. *Proceedings of the Royal Society B*.

@@

### 2023-09-22 news.qmd
update with new paper acceptance
fix date in news
update news feed

>>>>

<font color="#d08770">[September 22 2023].</font> **New award**. Congratulations to Daniel Deletsu who was awarded a 2-year Master's scholarship from the Heart and Stroke Foundation of Canada, Brain Canada Foundation, and the Canadian Institutes of Health Research.

<font color="#d08770">[September 6 2023].</font> **Paper accepted**.   Roth, A.M., Calalo, J.A., Lokesh, R., Sullivan, S.R., Grill, S., Jeka, J.J., van der Kooij, K., Carter, M.J, & Cashaback, J.G.A. Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds. *Proceedings of the Royal Society B*.
